Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-06-10 thesis/chapters/ch_conclusion.tex
draft of next steps for feedback physics comparison

>>>>

In addition, this work can be readily extended to further investigate how feedback governs the evolution of dwarf galaxies. We have already produced a suite of comparison simulations at a factor two lower resolution (3.6~pc) than our fiducial resolution, turning on and off each individual feedback process to understand the significance and characterize the mechanism by which each operates to regulate star formation, drive galactic winds, and govern chemical evolution. The feedback tested here includes supernovae, stellar ionizing radiation, photoelectric heating, Lyman-Werner radiation, and radiation pressure. The suite contains simulations including ``all-but-one" of each process, in addition to several combinations where multiple effects are excluded, and a set where the effectiveness of radiation pressure is artificially increased and decreased. Comparing the evolution of these dwarfs to our fiducial simulations presented in this \dissertation will improve our understanding of these processes, building upon previous works that have conducted similar studies in more massive dwarf galaxies \citep{Hu2016,Hu2017,Forbes2016,Hopkins2018}.
